TensorAlloy: an automatic atomistic neural network program for alloys

### 2019-08-20 doc/papers/nn/manuscript.tex
Switch to the CPC latex format.

\documentclass[preprint]{revtex4-2}

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external
\raggedbottom           % don't add extra vertical space
\begin{comment}
\pagestyle{empty}       % use if page numbers not wanted
\end{comment}

\bibliographystyle{apsrev4-2}

@@

\title{
    TensorAlloy: an automatic atomistic neural network program for alloys
}
\author{Xin Chen}
\author{Xing-Yu Gao}
\author{Ya-Fan Zhao}
\author{De-Ye Lin}
\email{lindeye0716@163.com}
\author{Wei-Dong Chu}
\author{Hai-Feng Song}
\email{song\_haifeng@iapcm.ac.cn}
\affiliation{
    Institute of Applied Physics and Computational Mathematics, 
    Beijing 100088, China}
\affiliation{
    CAEP Software Center for High Performance Numerical Simulation, 
    Beijing 100088, China}

@@

\maketitle

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Section 1. Introduction
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\newpage

\section{Introduction}

@@

This paper is organized as follows. Section \ref{section:theory} introduces the 
theory of the symmetry function descriptor and the ANN framework. Section 
\ref{section:method} describes the virtual atom approach and the modified ANN 
model used by TensorAlloy. Section \ref{section:discussions} demostrates 
the performances of TensorAlloy on two public datasets. The appendix 
\ref{section:appendix} gives derivation and implementation details of key 
routines of VAP. The full implementation and demo codes can be obtained from 
GitHub (https://github.com/Bismarrck/vap) freely.

@@

The Ni-Mo binary alloy system will be used as the example to show our 
algorithms. The original dataset (SNAP) is published by Shyue Ping 
Ong\cite{SNAP_2018}. 
For simplicity, only radial symmetry function related algorithms are 
visualized in the figures. Python3.7 implementations of key algorithms and 
functions are given in the appendix. A full demo (including the alloy datasets) 
can be obtained from GitHub freely (https://github.com/Bismarrck/vap).

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.1
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
\centering
\includegraphics[scale=0.68]{figures/Fig1.pdf}
\caption{\label{fig:program_design} The general design of TensorAlloy. 
\textbf{(1)} demonstrates the training phase while \textbf{(2)} represents the 
prediction phase.
}
\end{figure}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.5
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
\centering
\includegraphics[scale=0.95]{figures/Fig5.pdf}
\caption{\label{fig:Fig5} The calculation of 
$\mathbf{G}^{(2)}((\eta, \omega)_{\tau})$ from $\mathbf{r}^{\mathrm{GSL}}$. 
}
\end{figure}

@@

    \item[1.]
    The first step is applying Equation \ref{eq:g2} on 
    $\mathbf{r}^{\mathrm{GSL}}$ with the given $\tau$-th $(\eta, \omega)$ pair 
    to obtain raw descriptors $g^{\mathrm{GSL}}_{2}((\eta, \omega)_{\tau})$. 
    $g^{\mathrm{GSL}}_{2}((\eta, \omega)_{\tau})$ is a vector of length 
    $\nijmax$ and its last ($\nijmax - N_{ij}$) components are dummy values.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.6
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
\centering
\includegraphics[scale=0.54]{figures/qm7_speed.pdf}
\caption{\label{fig:benchmark_qm7} 
\textbf{a)} The curves of training speed (structures per second) vs batch sizes. 
\textbf{b)} The curves of test MAE (meV/atom) vs training time (GPU hour) using 
different settings.
\textbf{c)} The curves of test MAE (meV/atom) vs NN models. 
}
\end{figure}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table. 3
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table}[h]
\centering
\begin{tabular}{cccc|ccc|cc}
\hline
 & \multicolumn{3}{c|}{Energy (meV/atom)} & \multicolumn{3}{c|}{Force (eV/\AA)}
 & \multicolumn{2}{c}{Stress (GPa)} \\
\hline
NN Model & Mo & Ni & Ni-Mo & Mo & Ni & Ni-Mo & Mo & Ni-Mo \\
\hline
Mo & 4.9 (13.2) & & 16.5 (16.2) & 0.19 (0.25) & & 0.28 (0.29) & 0.24 (0.87) 
   & 0.75 \\
Ni & & 1.2 (1.2) & 4.5 (7.9) & & 0.04 (0.05) & 0.07 (0.11) & & 0.83 \\
Ni$_4$Mo & & & 4.1 (4.0) & & & 0.09 (0.14) & & 0.98 \\ 
Ni$_3$Mo & & & 4.5 (5.2) & & & 0.11 (0.16) & & 1.19 \\
Ni$_{\mathrm{Mo}}$ & & & 12.9 (22.7) & & & 0.09 (0.13) & & 0.34 \\
Mo$_{\mathrm{Ni}}$ & & & 12.9 (33.9) & & & 0.12 (0.55) & & 0.45 \\
Overall & & & 10.8 (22.5) & & & 0.11 (0.23) & & 0.59 \\
\hline
\end{tabular}

\caption{\label{table:MAE}
Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
stress (GPa) relative to DFT for TensorAlloy-trained models and their
corresponding SNAP benchmarks (bracket)}
\end{table}

Table \ref{table:MAE} summarizes the energy, force and stress prediction 
performances of TensorAlloy-trained models compared with their corresponding 
SNAP benchmarks. The original SNAP formalism contains both radial and angular 
interactions. However, in most cases, the radial-only TensorAlloy-trained 
models can significantly outperform corresponding SNAP models. The trainings of 
these models are also very fast. All these models are trained within 2 GPU hours
on our workstation.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.7
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.64]{figures/Prediction-speed.pdf}
\caption{\label{fig:prediction_speed} Benchmarks of the \textbf{NN}(Mo-Ni) model 
in the prediction phase. The test structures are (MoNi)$_{x}$ where 
$x$ = $10^3, 15^3, 20^3, 25^3, 30^3, 35^3, 40^3$. The left figure \textbf{a)} 
demonstrates the overall time and the right figure \textbf{b)} compares the 
'Graph' time with/out GPU. Blue bars indicate the elapsed time (in seconds) for 
finding neighbors, orange bars denote the time for initializing VAP-GSL arrays 
and green bars and the numbers above represents the graph execution time (used 
for obtaining energy, forces and stress).
}
\end{figure}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.8
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.8]{figures/Ni_EoS.pdf}
\caption{\label{fig:energy_volume_Ni} The energy vs volume curves of fcc Ni for
the DFT, Ni and Ni-Mo models.}
\end{figure}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.9
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.8]{figures/Ni_surface_energy.pdf}
\caption{\label{fig:surface_energy_Ni} Surface formation energies ($J/m^2$) of 
different Ni surfaces calculated by DFT, Ni and Ni-Mo models}
\end{figure}

The benchmark function and the trained models can be accessed from the VAP 
GitHub repo (https://github.com/Bismarrck/vap) freely.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% References
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\bibliography{manuscript.bib}

@@

\begin{verbatim}
def get_g4_map(atoms: Atoms,
               g2_map: dict,
               interactions: list,
               offsets: np.ndarray,
               vap: VirtualAtomMap,
               nijk_max: int,
               for_prediction=True):
    if for_prediction:
        iaxis = 0
    else:
        iaxis = 1
    g4_map = np.zeros((nijk_max, iaxis + 2), dtype=np.int32)
    ijk = np.zeros((nijk_max, 3), dtype=np.int32)
    n1 = np.zeros((nijk_max, 3), dtype=np.float32)
    n2 = np.zeros((nijk_max, 3), dtype=np.float32)
    n3 = np.zeros((nijk_max, 3), dtype=np.float32)
    symbols = atoms.get_chemical_symbols()
    indices = {}
    vectors = {}
    for i, atom_gsl_i in enumerate(g2_map["g2.ilist"]):
        if atom_gsl_i == 0:
            break
        if atom_gsl_i not in indices:
            indices[atom_gsl_i] = []
            vectors[atom_gsl_i] = []
        indices[atom_gsl_i].append(g2_map["g2.jlist"][i])
        vectors[atom_gsl_i].append(g2_map["g2.shift"][i])
    count = 0
    for atom_gsl_i, nl in indices.items():
        atom_local_i = vap.reverse_map[atom_gsl_i]
        symboli = symbols[atom_local_i]
        prefix = '{}'.format(symboli)
        for j in range(len(nl)):
            atom_vap_j = nl[j]
            atom_local_j = vap.reverse_map[atom_vap_j]
            symbolj = symbols[atom_local_j]
            for k in range(j + 1, len(nl)):
                atom_vap_k = nl[k]
                atom_local_k = vap.reverse_map[atom_vap_k]
                symbolk = symbols[atom_local_k]
                interaction = '{}{}'.format(
                    prefix, ''.join(sorted([symbolj, symbolk])))
                ijk[count] = atom_gsl_i, atom_vap_j, atom_vap_k
                n1[count] = vectors[atom_gsl_i][j]
                n2[count] = vectors[atom_gsl_i][k]
                n3[count] = vectors[atom_gsl_i][k] - vectors[atom_gsl_i][j]
                index = interactions.index(interaction)
                g4_map[count, iaxis + 0] = atom_gsl_i
                g4_map[count, iaxis + 1] = offsets[index]
                count += 1
    return {"g4.v2g_map": g4_map,
            "g4.ij.ilist": ijk[:, 0], "g4.ij.jlist": ijk[:, 1],
            "g4.ik.ilist": ijk[:, 0], "g4.ik.klist": ijk[:, 2],
            "g4.jk.jlist": ijk[:, 1], "g4.jk.klist": ijk[:, 2],
            "g4.shift.ij": n1, "g4.shift.ik": n2, "g4.shift.jk": n3}
\end{verbatim}

@@

The demo script can be found on GitHub: https://github.com/Bismarrck/vap.

@@

    def __init__(self, rc, elements, eta=np.array([0.05, 4.0, 20.0, 80.0]),
                 omega=np.array([0.0]), beta=np.array([0.005, ]),
                 gamma=np.array([1.0, -1.0]), zeta=np.array([1.0, 4.0]),
                 angular=True, periodic=True):
        all_kbody_terms, kbody_terms, elements = \
            get_kbody_terms(elements, angular=angular)
        ndim, kbody_sizes = compute_dimension(
            all_kbody_terms, len(eta), len(omega), len(beta), len(gamma),
            len(zeta))
        self.rc = rc
        self.all_kbody_terms = all_kbody_terms
        self.kbody_terms = kbody_terms
        self.elements = elements
        self.n_elements = len(elements)
        self.periodic = periodic
        self.angular = angular
        self.kbody_sizes = kbody_sizes
        self.ndim = ndim
        self.kbody_index = {
            kbody_term: self.all_kbody_terms.index(kbody_term)
            for kbody_term in self.all_kbody_terms}
        self.offsets = np.insert(np.cumsum(kbody_sizes), 0, 0)
        self.radial_indices_grid = ParameterGrid({
            'eta': np.arange(len(eta), dtype=int),
            'omega': np.arange(len(omega), dtype=int)})
        self.angular_indices_grid = ParameterGrid({
            'beta': np.arange(len(beta), dtype=int),
            'gamma': np.arange(len(gamma), dtype=int),
            'zeta': np.arange(len(zeta), dtype=int)})
        self.initial_values = {'eta': eta, 'omega': omega, 'gamma': gamma,
                               'beta': beta, 'zeta': zeta}

@@

    def get_rij(self, positions, cells, ilist, jlist, shift, name):
        with tf.name_scope(name):
            dtype = positions.dtype
            Ri = self.gather_fn(positions, ilist, 'Ri')
            Rj = self.gather_fn(positions, jlist, 'Rj')
            Dij = tf.subtract(Rj, Ri, name='Dij')
            if self.periodic:
                pbc = self.get_pbc_displacements(shift, cells, dtype=dtype)
                Dij = tf.add(Dij, pbc, name='pbc')
            with tf.name_scope("safe_norm"):
                eps = tf.constant(1e-8, dtype=dtype, name='eps')
                rij = tf.sqrt(tf.reduce_sum(
                    tf.square(Dij, name='Dij2'), axis=-1) + eps)
                return rij, Dij

@@

    def split_descriptors(self, descriptors, features: dict):
        with tf.name_scope("Split"):
            row_split_sizes = self.get_row_split_sizes(features)
            row_split_axis = self.get_row_split_axis()
            column_split_sizes = self.get_column_split_sizes()
            column_split_axis = self.get_column_split_axis()
            splits = tf.split(
                descriptors, row_split_sizes, axis=row_split_axis,
                name='rows')[1:]
            atom_masks = tf.split(
                features['atom_masks'], row_split_sizes, 
                axis=row_split_axis,
                name='atom_masks')[1:]
            if len(self.elements) > 1:
                blocks = []
                for i in range(len(splits)):
                    element = self.elements[i]
                    size_splits, idx = column_split_sizes[element]
                    block = tf.split(splits[i],
                                     size_splits,
                                     axis=column_split_axis,
                                     name='{}_block'.format(element))[idx]
                    blocks.append(block)
            else:
                blocks = splits
            return dict(zip(self.elements, zip(blocks, atom_masks)))

@@

>>>>

%% This template can be used to write a paper for
%% Computer Physics Communications using LaTeX.
%% For authors who want to write a computer program description,
%% an example Program Summary is included that only has to be
%% completed and which will give the correct layout in the
%% preprint and the journal.
%% The `elsarticle' style is used and more information on this style
%% can be found at 
%% http://www.elsevier.com/wps/find/authorsview.authors/elsarticle.
%%
%%
%% \documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
\documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external

%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

%% This list environment is used for the references in the
%% Program Summary
%%
\newcounter{bla}
\newenvironment{refnummer}{%
\list{[\arabic{bla}]}%
{\usecounter{bla}%
 \setlength{\itemindent}{0pt}%
 \setlength{\topsep}{0pt}%
 \setlength{\itemsep}{0pt}%
 \setlength{\labelsep}{2pt}%
 \setlength{\listparindent}{0pt}%
 \settowidth{\labelwidth}{[9]}%
 \setlength{\leftmargin}{\labelwidth}%
 \addtolength{\leftmargin}{\labelsep}%
 \setlength{\rightmargin}{0pt}}}
 {\endlist}

\journal{Computer Physics Communications}

@@

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{TensorAlloy: an automatic atomistic neural network program for alloys}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[a]{Xin Chen}
\author[a]{Xing-Yu Gao}
\author[b]{Ya-Fan Zhao}
\author[b]{De-Ye Lin\corref{author}}
\author[a]{Wei-Dong Chu}
\author[a,b]{Hai-Feng Song\corref{author}}

\cortext[author] {Corresponding author.
\\\textit{E-mail address:} lindeye0716@163.com}
\address[a]{Institute of Applied Physics and Computational Mathematics, 
Beijing 100088, China}
\address[b]{CAEP Software Center for High Performance Numerical Simulation, 
Beijing 100088, China}

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Machine Learning; Alloy; Materials Modeling; Computational Physics; 
Neural Network

\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

% Computer program descriptions should contain the following
% PROGRAM SUMMARY.

{\bf PROGRAM SUMMARY} \\
\begin{small}
\noindent
{\em Program Title: TensorAlloy} \\
{\em Licensing provisions(please choose one): Apache-2.0}     \\
{\em Programming language: Python 3.7}                        \\
{\em Supplementary material:}                                 \\
{\em Journal reference of previous version:}                  \\
{\em Does the new version supersede the previous version?:}   \\
{\em Reasons for the new version:} \\
{\em Summary of revisions:}*\\
{\em Nature of problem:} \\
  Modeling interatomic interactions with the symmetry function descriptor based
  atomistic neural networks.
{\em Solution method:} \\
  The TensorAlloy program is built upon TensorFlow and the virtual-atom 
  approach. TensorAlloy can build direct computation graph from atomic positions 
  to total energy. Atomic forces and virial stress tensors are handled by 
  TensorFlow automatically and efficiently.
{\em Additional comments including Restrictions and Unusual features}\\
  This program needs TensorFlow 1.13.*. Neither newer or older TensorFlow is 
  supported. \\
\end{small}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Section 1. Introduction
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\section{Introduction}

@@

This paper is organized as follows. Section \ref{section:theory} introduces the 
theory of the symmetry function descriptor and the ANN framework. Section 
\ref{section:method} describes the virtual atom approach and the modified ANN 
model used by TensorAlloy. Section \ref{section:discussions} demostrates 
the performances of TensorAlloy on two public datasets. The appendix 
\ref{section:appendix} gives derivation and implementation details of key 
routines of VAP.

@@

The Ni-Mo binary alloy system will be used as the example to show our 
algorithms. The original dataset (SNAP) is published by Shyue Ping 
Ong\cite{SNAP_2018}. 
For simplicity, only radial symmetry function related algorithms are 
visualized in the figures. Python3.7 implementations of key algorithms and 
functions are given in the appendix.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.1
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
\centering
\includegraphics[scale=0.55]{figures/Fig1.pdf}
\caption{\label{fig:program_design} The general design of TensorAlloy. 
\textbf{(1)} demonstrates the training phase while \textbf{(2)} represents the 
prediction phase.
}
\end{figure}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.5
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
\centering
\includegraphics[scale=0.75]{figures/Fig5.pdf}
\caption{\label{fig:Fig5} The calculation of 
$\mathbf{G}^{(2)}((\eta, \omega)_{\tau})$ from $\mathbf{r}^{\mathrm{GSL}}$. 
}
\end{figure}

@@

    \item[1.]
    The first step is applying Equation \ref{eq:g2} on 
    $\mathbf{r}^{\mathrm{GSL}}$ with the given $\tau$-th $(\eta, \omega)$ pair 
    to obtain $g^{\mathrm{GSL}}_{2}((\eta, \omega)_{\tau})$. 
    $g^{\mathrm{GSL}}_{2}((\eta, \omega)_{\tau})$ is a vector of length 
    $\nijmax$ and its last ($\nijmax - N_{ij}$) components are dummy values.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.6
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
\centering
\includegraphics[scale=0.44]{figures/qm7_speed.pdf}
\caption{\label{fig:benchmark_qm7} 
\textbf{a)} The curves of training speed (structures per second) vs batch sizes. 
\textbf{b)} The curves of test MAE (meV/atom) vs training time (GPU hour) using 
different settings.
\textbf{c)} The curves of test MAE (meV/atom) vs NN models. 
}
\end{figure}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table. 3
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table}[h]
\centering
\begin{tabular}{cccc}
\hline
Subset & Energy (meV/atom) & Force (eV/\AA) & Stress (GPa) \\
\hline
Mo & 16.5 (16.2) & 0.28 (0.29) & 0.75 \\
Ni & 4.5 (7.9)   & 0.07 (0.11) & 0.83 \\
Ni$_4$Mo & 4.1 (4.0) & 0.09 (0.14) & 0.98 \\ 
Ni$_3$Mo & 4.5 (5.2) & 0.11 (0.16) & 1.19 \\
Ni$_{\mathrm{Mo}}$ & 12.9 (22.7) & 0.09 (0.13)& 0.34 \\
Mo$_{\mathrm{Ni}}$ & 12.9 (33.9) & 0.12 (0.55)& 0.45 \\
Overall & 10.8 (22.5)& 0.11 (0.23) & 0.59 \\
\hline
\end{tabular}
\caption{\label{table:MAE}
Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
stress (GPa) relative to DFT of each subset for the binary Mo-Ni model and the
corresponding SNAP benchmarks (bracket)}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{ccc|cc|c}
\hline
  & \multicolumn{2}{c|}{Energy (meV/atom)} & \multicolumn{2}{c|}{Force (eV/\AA)}
  & Stress (GPa) \\
\hline
Elementary Model & Mo & Ni & Mo & Ni & Mo \\
\hline
Mo & 4.9 (13.2) & & 0.19 (0.25) & & 0.24 (0.87) \\
Ni & & 1.2 (1.2) & & 0.04 (0.05) & \\
\hline
\end{tabular}
\caption{\label{table:MAE1}
Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
stress (GPa) relative to DFT for the two elementary models (Ni, Mo) and their
corresponding SNAP benchmarks (bracket)}
\end{table}

Table \ref{table:MAE} and \ref{table:MAE1} summarizes the energy, force and 
stress prediction performances of our trained models compared with their 
corresponding SNAP benchmarks. 
The original SNAP formalism contains both radial and angular 
interactions. However, in most cases, the radial-only TensorAlloy-trained 
models can significantly outperform corresponding SNAP models. The trainings of 
these models are also very fast. All these models are trained within 2 GPU hours
on our workstation.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.7
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.5]{figures/Prediction-speed.pdf}
\caption{\label{fig:prediction_speed} Benchmarks of the \textbf{NN}(Mo-Ni) model 
in the prediction phase. The test structures are (MoNi)$_{x}$ where 
$x$ = $10^3, 15^3, 20^3, 25^3, 30^3, 35^3, 40^3$. The left figure \textbf{a)} 
demonstrates the overall time and the right figure \textbf{b)} compares the 
'Graph' time with/out GPU. Blue bars indicate the elapsed time (in seconds) for 
finding neighbors, orange bars denote the time for initializing VAP-GSL arrays 
and green bars and the numbers above represents the graph execution time (used 
for obtaining energy, forces and stress).
}
\end{figure}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.8
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.65]{figures/Ni_EoS.pdf}
\caption{\label{fig:energy_volume_Ni} The energy vs volume curves of fcc Ni for
the DFT, Ni and Ni-Mo models.}
\end{figure}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Fig.9
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.65]{figures/Ni_surface_energy.pdf}
\caption{\label{fig:surface_energy_Ni} Surface formation energies ($J/m^2$) of 
different Ni surfaces calculated by DFT, Ni and Ni-Mo models}
\end{figure}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% References
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\bibliographystyle{elsarticle-num}
\bibliography{manuscript.bib}

@@

\begin{verbatim}
def get_g4_map(atoms: Atoms,
               g2_map: dict,
               interactions: list,
               offsets: np.ndarray,
               vap: VirtualAtomMap,
               nijk_max: int,
               for_prediction=True):
    if for_prediction:
        iaxis = 0
    else:
        iaxis = 1
    g4_map = np.zeros((nijk_max, iaxis + 2), dtype=np.int32)
    ijk = np.zeros((nijk_max, 3), dtype=np.int32)
    n1 = np.zeros((nijk_max, 3), dtype=np.float32)
    n2 = np.zeros((nijk_max, 3), dtype=np.float32)
    n3 = np.zeros((nijk_max, 3), dtype=np.float32)
    symbols = atoms.get_chemical_symbols()
    indices = {}
    vectors = {}
    for i, atom_gsl_i in enumerate(g2_map["g2.ilist"]):
        if atom_gsl_i == 0:
            break
        if atom_gsl_i not in indices:
            indices[atom_gsl_i] = []
            vectors[atom_gsl_i] = []
        indices[atom_gsl_i].append(g2_map["g2.jlist"][i])
        vectors[atom_gsl_i].append(g2_map["g2.shift"][i])
    count = 0
    for atom_gsl_i, nl in indices.items():
        atom_local_i = vap.reverse_map[atom_gsl_i]
        symboli = symbols[atom_local_i]
        prefix = '{}'.format(symboli)
        for j in range(len(nl)):
            atom_vap_j = nl[j]
            atom_local_j = vap.reverse_map[atom_vap_j]
            symbolj = symbols[atom_local_j]
            for k in range(j + 1, len(nl)):
                atom_vap_k = nl[k]
                atom_local_k = vap.reverse_map[atom_vap_k]
                symbolk = symbols[atom_local_k]
                interaction = '{}{}'.format(
                    prefix, ''.join(sorted([symbolj, symbolk])))
                ijk[count] = atom_gsl_i, atom_vap_j, atom_vap_k
                n1[count] = vectors[atom_gsl_i][j]
                n2[count] = vectors[atom_gsl_i][k]
                n3[count] = n2[count] - n1[count]
                index = interactions.index(interaction)
                g4_map[count, iaxis + 0] = atom_gsl_i
                g4_map[count, iaxis + 1] = offsets[index]
                count += 1
    return {"g4.v2g_map": g4_map,
            "g4.ij.ilist": ijk[:, 0], "g4.ij.jlist": ijk[:, 1],
            "g4.ik.ilist": ijk[:, 0], "g4.ik.klist": ijk[:, 2],
            "g4.jk.jlist": ijk[:, 1], "g4.jk.klist": ijk[:, 2],
            "g4.shift.ij": n1, "g4.shift.ik": n2, "g4.shift.jk": n3}
\end{verbatim}

@@

@@

    def __init__(self, rc, elements, eta=np.array([0.05, 4, 20, 80]),
                 omega=np.array([0.0]), beta=np.array([0.005, ]),
                 gamma=np.array([1.0, -1.0]), zeta=np.array([1.0, 4.0]),
                 angular=True, periodic=True):
        all_kbody_terms, kbody_terms, elements = \
            get_kbody_terms(elements, angular=angular)
        ndim, kbody_sizes = compute_dimension(
            all_kbody_terms, len(eta), len(omega), len(beta), len(gamma),
            len(zeta))
        self.rc = rc
        self.all_kbody_terms = all_kbody_terms
        self.kbody_terms = kbody_terms
        self.elements = elements
        self.n_elements = len(elements)
        self.periodic = periodic
        self.angular = angular
        self.kbody_sizes = kbody_sizes
        self.ndim = ndim
        self.kbody_index = {
            kbody_term: self.all_kbody_terms.index(kbody_term)
            for kbody_term in self.all_kbody_terms}
        self.offsets = np.insert(np.cumsum(kbody_sizes), 0, 0)
        self.radial_indices_grid = ParameterGrid({
            'eta': np.arange(len(eta), dtype=int),
            'omega': np.arange(len(omega), dtype=int)})
        self.angular_indices_grid = ParameterGrid({
            'beta': np.arange(len(beta), dtype=int),
            'gamma': np.arange(len(gamma), dtype=int),
            'zeta': np.arange(len(zeta), dtype=int)})
        self.initial_values = {'eta': eta, 'omega': omega, 
                               'gamma': gamma,
                               'beta': beta, 'zeta': zeta}

@@

    def get_rij(self, positions, cells, ilist, jlist, shift, name):
        with tf.name_scope(name):
            dtype = positions.dtype
            Ri = self.gather_fn(positions, ilist, 'Ri')
            Rj = self.gather_fn(positions, jlist, 'Rj')
            Dij = tf.subtract(Rj, Ri, name='Dij')
            if self.periodic:
                pbc = self.get_pbc_displacements(shift, cells, dtype)
                Dij = tf.add(Dij, pbc, name='pbc')
            with tf.name_scope("safe_norm"):
                eps = tf.constant(1e-8, dtype=dtype, name='eps')
                rij = tf.sqrt(tf.reduce_sum(
                    tf.square(Dij, name='Dij2'), axis=-1) + eps)
                return rij, Dij

@@

    def split_descriptors(self, descriptors, features: dict):
        with tf.name_scope("Split"):
            row_split_sizes = self.get_row_split_sizes(features)
            row_split_axis = self.get_row_split_axis()
            column_split_sizes = self.get_column_split_sizes()
            column_split_axis = self.get_column_split_axis()
            splits = tf.split(
                descriptors, row_split_sizes, axis=row_split_axis,
                name='rows')[1:]
            atom_masks = tf.split(
                features['atom_masks'], row_split_sizes, 
                axis=row_split_axis,
                name='atom_masks')[1:]
            if len(self.elements) > 1:
                blocks = []
                for i in range(len(splits)):
                    element = self.elements[i]
                    size_splits, idx = column_split_sizes[element]
                    block = tf.split(splits[i],
                                     size_splits,
                                     axis=column_split_axis,
                                     name=f'{element}_block')[idx]
                    blocks.append(block)
            else:
                blocks = splits
            return dict(zip(self.elements, zip(blocks, atom_masks)))

@@

%%
%% End of file
